Indexes measures for oak decline severity using phenotypic descriptors

### 2019-11-11 manuscript/figures.Rmd
added phenotypic descriptor table

```{r DAI_response_surfaces,fig.height = 8,fig.cap='DAI response surfaces for simulated descriptor values from trained Random Forest models. All other descriptors were set at the values of those of the trees with the lowest PDI used for trainig the models',cache=FALSE}
source('../code/DAI_response_surfaces.R')
grid.arrange(DAI_response_plot$`a)`,DAI_response_plot$`b)`,DAI_response_plot$`c)`,DAI_response_plot$`d)`,DAI_response_plot$`e)`,DAI_response_plot$`f)`,DAI_response_plot$legend,ncol = 3,layout_matrix = rbind(c(1,4,7),c(2,5,7),c(3,6,7)),widths = c(4,4,1),newpage = F)
```

>>>>

```{r DAI_response_surfaces,fig.height = 8,fig.cap='DAI response surfaces for simulated descriptor values from trained Random Forest models. All other descriptors were set at the values of those of the trees with the lowest PDI used for trainig the models'}
source('../code/DAI_response_surfaces.R')
grid.arrange(DAI_response_plot$`a)`,DAI_response_plot$`b)`,DAI_response_plot$`c)`,DAI_response_plot$`d)`,DAI_response_plot$`e)`,DAI_response_plot$`f)`,DAI_response_plot$legend,ncol = 3,layout_matrix = rbind(c(1,4,7),c(2,5,7),c(3,6,7)),widths = c(4,4,1),newpage = F)
```

### 2019-11-11 outline/outline.Rmd
added phenotypic descriptor table

---
title: "Indexes measures for oak decline severity using phenotypic descriptors"
output: word_document
---

@@

**Figure 1:** 
    - a) Site differences MDS plot
    - b) Site difference feature importance

>>>>

---
title: "Indexes measures for oak decline severity using phenotypic descriptors"
output: pdf_document
---

@@

**Table 2:** Resampled index performance results

**Figure 1:**

  - a) Site differences MDS plot
  - b) Site difference feature importance
